\documentclass[a4paper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{cv,booktabs,fontawesome}

% Change color to blue
\def\headcolor{\color[rgb]{0,0,0.5}}

% Space before section headings
\titlespacing{\section}{0pt}{2ex}{1ex}

\name{Lev Matyushkin}

\info{\faicon{map-marker} & Department of Micro \& Nanoelectronics, ETU
                               Saint-Petersburg Electrotechnical University, Russia\\
      \faicon{phone}      & +7 951 6749577\\
}


\usepackage[backend=biber]{biblatex}
\addbibresource{Matyushkin_en_best.bib}

%\renewcommand{\refname}{Best papers}


\begin{document}



\maketitle

\section{Education and Qualifications}

~\begin{tabular}{llll}
2010 & B.Sc. & Electronics and Microelectronics & ETU\\
2012 & M.Sc. & Nanotechnology and Diagnostics & ETU\\
2018 & Ph.D. & Semiconductor Technology & ETU
\end{tabular}


\section{Positions}

~\begin{tabular}{lP{15cm}}

2013--& \textbf{Teaching Assistant}, Department of Micro- and Nanoelectronics, ETU.\\
2018--& \textbf{Researcher}, Micro and Nanodiagnostics Center, ETU.
\end{tabular}

\section{Grants, awards and scholarships}

\begin{enumerate}
\item[2017] ETU Personal Grant for Scientific Projects of Young Researchers.
\item[2016] Grant of Russian Foundation for Basic Research on additive technologies "Creation of metal coatings on porous materials by additive technologies".
\item[2015] The Winner of Competition of Research and Innovation Projects of Graduate Students, Young Researchers and Teachers ETU "LETI".
\item[2014] Grant of Russian Science Foundation "Colloidal quantum dots as biomarkers for scientific research of pathological processes of the female reproductive system".
\item[2014] Grant of Russian Foundation for Basic Research "Development of a photometric method for express diagnostics of nanoporous membranes based on por-Al$_2$O$_3$".
\item[2014] Grant of Russian Foundation for Basic Research "Investigation of the structure of porous materials from the absorption spectra of lead chalcogenide nanoparticles introduced into the pores".
\item[2013] The Winner of Youth Research and Innovation Competition U.M.N.I.K.
\item[2012] Grant of Federal Target Program "Research and Scientific-Pedagogical Personnel of Innovative Russia".
\item[2012] Diploma of the 1st degree on the results of competition for the best master's thesis in 2011/2012 academic year.

\end{enumerate}

\section{Research}

\begin{itemize}\parskip=0cm
\item Since 2012 I have authored 117 papers, chapters or books on the synthesis and study of colloidal quantum dots and thin films of semiconductor materials. 48 publications are in Web of Science and Scopus databases (3 Q1 articles). The list of selected publications appears on the following page.
\item My current research involves the effects of plasmon nanoparticles and quantum dots composite systems.
\end{itemize}

%\enlargethispage*{0.9cm}

%\newpage
\nocite{*}
\printbibliography

\end{document}
